Supplementary material

### 2018-06-07 Manuscript/ms.tex
Updating the abstract

Our ability to effectively prevent the transmission of the dengue virus through targeted control of its vector, \emph{Aedes aegypti}, depends critically on our understanding of the link between mosquito abundance and human disease risk.
The mosquito and clinical surveillance data necessary to elucidate this link are widely collected, but have yet to be coupled with a modeling framework that accounts for the complex non-linear mechanisms involved in transmission, in particular the critical bottleneck imposed by mosquito mortality.
We developed a differential equation model of dengue transmission and embedded it in a Bayesian hierarchical framework that allowed us to estimate latent time series of mosquito demographic rates from mosquito trap counts and dengue case reports from the city of Vitoria, Brazil.
We used the fitted model to explore the optimal timing of targeted adult control during the year.
We found that control was most effective when deployed in the third week of the year, as mosquito abundance neared its peak and dengue transmission began to ramp up.
Intervening at this time disrupts transmission and prevents the amplification and feedback that leads to large outbreaks of disease, an insight not possible without the underlying mechanistic model.
Though the ability of mosquito surveillance to predict human disease is often limited, this highlights the utility of this surveillance when integrated into a larger modeling framework.
Grounding this modeling famework in the actual mechanisms of transmission will help to establish more effective and efficient dengue control policies that allow us to better target mosquitoes that are most responsible for continuing disease spread.

>>>>

Our ability to effectively prevent the transmission of the dengue virus through targeted control of its vector, \emph{Aedes aegypti}, depends critically on our understanding of the link between mosquito abundance and human disease risk.
The mosquito and clinical surveillance data necessary to elucidate this link are widely collected, but have yet to be coupled with a modeling framework that accounts for the complex non-linear mechanisms involved in transmission, in particular the critical bottleneck imposed by mosquito mortality.
We developed a differential equation model of dengue transmission and embedded it in a Bayesian hierarchical framework that allowed us to estimate latent time series of mosquito demographic rates from mosquito trap counts and dengue case reports from the city of Vitoria, Brazil.
We used the fitted model to explore the effect of adult mosquito control on the disease burden in each year, while taking advantage of the Bayesian framework to carry through uncertainty from the posterior distributions of model parameters and mosquito demographic rates.
We found that control deployed between 30 and 40 weeks prior to the start of the year was most effective at preventing cases in that year. 
This timing generally coincided with a local minimum in the size of the susceptible pool.
Uncertainty in the effectiveness of control interventions was driven largely by uncertainty in the period of cross-immunity, with longer periods of cross-immunity leading to less effective control.
Understanding the dynamics of temporary human immunity is thus critical for understanding the effect of mosquito control efforts on human disease.
